Clustering: A pipeline to analyse time-course gene expression data

### 2019-04-24 scripts/03_clustering.Rmd
Smooth plotting is finally working
FIX Colors now correspond to the right conditions
ENH Now performing prediction step in stability analysis

```{r fig.height=8, fig.width=8}
moanin:::plot_centroids(centroids, splines_model,
			colors=as.vector(unlist(ann_colors["Group"])),
			smooth=FALSE)
```

@@

>>>>

```{r fig.height=8, fig.width=8}
moanin:::plot_centroids(centroids, splines_model,
			colors=ann_colors$Group,
			smooth=TRUE)
```

@@

### Looking at the stability of the clustering

```{r fig.width=6, fig.height=4}
library(pheatmap)
stability_5 = read.table("results/stability_5.tsv", sep="\t")
consensus_matrix_stability_5 = moanin::consensus_matrix(stability_5)
pheatmap::pheatmap(consensus_matrix_stability_5[1:1000, 1:1000], symm=TRUE,
		   treeheight_row=0, treeheight_col=0)

stability_20 = read.table("results/stability_20.tsv", sep="\t")
consensus_matrix_stability_20 = moanin::consensus_matrix(stability_20)
pheatmap::pheatmap(consensus_matrix_stability_20[1:1000, 1:1000], symm=TRUE,
		   treeheight_row=0, treeheight_col=0)
